Efficient pedigree recording for fast population genetics simulation

### 2017-12-27 forwards_paper.tex
delete SI section and have the figs as part of appendix
define the notation close to where first used
add comment

We use $\randomuniform(A)$ to denote an element of the set $A$ chosen uniformly at random
(and all such instances are independent).
Given a node table $\Nt$, the function $\taddnode{\Nt, t}$
adds a new node to the table $\Nt$ with time $t$
and returns the ID of this new node.
Similarly, the function $\taddedge{\Et, \ell, r, p, c}$
adds a new edge $(\ell, r, p, c)$ to the edge table $\Et$.
The function $\tsimplify{P, \Nt, \Et}$ (described in section \ref{ss:simplify})
simplifies the history stored in the tables $\Nt$ and $\Et$
to the minimal information required to represent the genealogies of the list of node IDs $P$;
after simplification the nodes appearing in $P$ are relabeled $(0, 1, \ldots, |P|)$.
A step-by-step explanation follows the pseudocode.

@@

@@

\newpage
\clearpage
\section*{Supplementary Information}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}

>>>>

We use $\randomuniform(A)$ to denote an element of the set $A$ chosen uniformly at random
(and all such instances are independent).
Given a node table $\Nt$, the function $\taddnode{\Nt, t}$
adds a new node to the table $\Nt$ with time $t$
and returns the ID of this new node.
Similarly, the function $\taddedge{\Et, \ell, r, p, c}$
adds a new edge $(\ell\mathrm{eft}, r\mathrm{ight}, p\mathrm{arent}, c\mathrm{hild})$ to the edge table $\Et$.
The function $\tsimplify{P, \Nt, \Et}$ (described in section \ref{ss:simplify})
simplifies the history stored in the tables $\Nt$ and $\Et$
to the minimal information required to represent the genealogies of the list of node IDs $P$;
after simplification the nodes appearing in $P$ are relabeled $(0, 1, \ldots, |P|)$.
A step-by-step explanation follows the pseudocode.

@@

\krt{The following paragraph has a sentence mangling.  I think some comment is warrented about when it is useful to
record selected mutations, like for ancient samples?}

@@

%% \newpage
%% \clearpage
%% \section*{Supplementary Information}
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}
